\bf Supplementary Material to\\ ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2025-10-04 manuscript/reply2.tex

I would still like a little bit of clarification about the bias correction $K_n(x)$ versus the bias correction $C_n(x)$. I understand that $K_n(x)$, which the authors prescribe under the circular blocks bootstrap, is based on bootstrap expectations $E_*$ of the bootstrap parameter estimate as well as of the bootstrap empirical cdf. In contract, the bias term $C_n(x)$ is constructed using the empirical cdf and by plugging in the sample estimator of the parameter (so it does not involve bootstrap expectations).  This is explained in the added section, Section 2.4.  This much is clear. However, what is still not clear to me is WHY one should use the correction $K_n(x)$ instead of $C_n(x)$. The explanation in Section 2.4 is that the bootstrap expectations become "necessary only when serial dependence distorts the properties of $F_n(x)$".  But this statement is quite vague.  Also vague is the statement in the preceding sentence which says that the empirical cdf and the parameter estimate are "reliable" under independence -- suggesting that they are not "reliable" when there is serial dependence in the data.  But what does "reliable" mean? These estimators should be consistent (under mild conditions) in both settings.

@@

We thank the AE for this helpful comment. We have added a supplement
which includes a section on "Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness} Bias Correction". We re-ran the simulation study from the main
manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
The results are discussed in the supplement, and are alluded to in the main paper. Overall,
we find that there is no noticeable improvement in either size
or power when using the $K_n(x)$ bias correction, even for small sample
sizes. With these results, we recommend ........

@@

Thank you for the suggestion, these investigations have now been placed in the "Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with Block Size Calibration" of
the new supplement, and they are still referred to in
the main manuscript.

\begin{comment}
There is an odd typo on the bottom of page 9. It says "average empirical GXSdistribution function".
\end{comment}

Thank you for pointing this out. This typo has been
corrected to "average empirical distribution function" in the manuscript.

>>>>

I would still like a little bit of clarification about the bias
correction $K_n(x)$ versus the bias correction $C_n(x)$. I understand
that $K_n(x)$, which the authors prescribe under the circular blocks
bootstrap, is based on bootstrap expectations $E_*$ of the bootstrap
parameter estimate as well as of the bootstrap empirical cdf. In
contract, the bias term $C_n(x)$ is constructed using the empirical
cdf and by plugging in the sample estimator of the parameter (so it
does not involve bootstrap expectations).  This is explained in the
added section, Section 2.4.  This much is clear. However, what is
still not clear to me is WHY one should use the correction $K_n(x)$
instead of $C_n(x)$. The explanation in Section 2.4 is that the
bootstrap expectations become ``necessary only when serial dependence
distorts the properties of $F_n(x)$''.  But this statement is quite
vague.  Also vague is the statement in the preceding sentence which
says that the empirical cdf and the parameter estimate are ``reliable''
under independence -- suggesting that they are not ``reliable'' when
there is serial dependence in the data.  But what does ``reliable''
mean? These estimators should be consistent (under mild conditions) in
both settings.

@@

We thank the AE for this helpful comment. We have added a supplement
which includes a section on ``Performance of Nonparametric
Block Bootstrap Kolmogorov-Smirnov Test with \citet{babu2004goodness}
Bias Correction''. We re-ran the simulation study from the main
manuscript, but we replaced the $K_n(x)$ bias correction with $C_n(x)$.
The results are discussed in the supplement, and are alluded to in the
main paper. Overall, we find that there is no noticeable improvement
in either size or power when using the $K_n(x)$ bias correction, even
for small sample sizes. With these results, we recommend ........

@@

Thank you for the suggestion, these investigations have now been
placed in the ``Performance of Nonparametric Block Bootstrap
Kolmogorov-Smirnov Test with Block Size Calibration'' of the new
supplement, and they are still referred to in the main manuscript.

\begin{comment}
There is an odd typo on the bottom of page 9. It says ``average
empirical GXSdistribution function''
\end{comment}

Thank you for pointing this out. This typo has been
corrected to ``average empirical distribution function'' in the manuscript.
